Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Add Parish, Müller references
Update todo
Rebuild report
References in alphabetical order
Collision study, disposition

@@

@@

% Thursday:
% TODO: Write introduction section
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
    % TODO: Introduction references
% TODO: Write Collision study implementation section
    % TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

@@

\bibitem{arkin-91}
Arkin, Esther \& Chew, L. \& Huttenlocher, Daniel \& Kedem, Klara \& Mitchell, Joseph. (1991). An Efficiently Computable Metric for Comparing Polygonal Shapes. IEEE Transaction Pattern Analysis and Machine Intelligence 13. 209-216.

@@

>>>>

\subsection{Road widths and properties}

@@

\subsection{Feature overlap algorithm}

Outline of the feature overlap algorithm (Go over all features)
Since only road collisions are of interests, all roads were added to a queue and gone over one by one.

The boundary polygon of the buildings are extracted, as well as the polylines of the roads.

To speed up the collision checking process, a geometric hashing solution was developed.
This way feature collision lookup could be made without comparing a feature to all other available features, but instead from a selection of the closest candidates.
The hash bucket size was 230 meters and a feature could be in multiple hash buckets.

Special cases: Where two roads intersect though they share a node.
Then this is a natural connection in the road network and should not be counted as a problematic case of feature overlap.
Also ignored collisions between tunnels and bridges and other roads since these are of different heights.
These were identified by looking at feature attributes in OSM.
Any roads that were represented as polygons or multipolygons instead of plylines were also excluded from the study.

\subsection{Projected edge distance}

Outline of the minimum edge distance algorithm.

@@

% Thursday:
% TODO: Write introduction section
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
    % TODO: read Biljecki
    % TODO: read Vanega
% TODO: Write Collision study implementation section
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

@@

\bibitem{arkin-91}
Arkin, E., Chew, L., Huttenlocher, D., Kedem, K. and Mitchell, J. (1991). An Efficiently Computable Metric for Comparing Polygonal Shapes. IEEE Transaction Pattern Analysis and Machine Intelligence 13. 209-216.

@@

\bibitem{muller-06}
Müller, P., Wonka, P., Haegler, S., Ulmer, A. and Van Gool, L. (2006). Procedural modeling of buildings. In ACM SIGGRAPH 2006 Papers, 614-623.

\bibitem{parish-01}
Parish, Y. I., and Müller, P. (2001) Procedural modeling of cities. In Proceedings of the 28th annual conference on Computer graphics and interactive techniques, SIGGRAPH, 12-17 August 2001, Los Angeles, Calif., 301-308.
